
readr
======================================
The goal of readr is to provide a fast and friendly way to read tabular data into R.  

The most important functions are:

- Read delimited files: read_delim(), read_csv(), read_tsv(), read_csv2().
- Read fixed width files: read_fwf(), read_table().
- Read lines: read_lines().
- Read whole file: read_file().
- Re-parse existing data frame: type_convert().

#### Installation

readr is now available from CRAN.

```{r}
install.packages("readr")
You can try out the dev version with:

# install.packages("devtools")
devtools::install_github("hadley/readr")
```
#### Usage

```{r}
library(readr)
library(dplyr)

mtcars_path <- tempfile(fileext = ".csv")
write_csv(mtcars, mtcars_path)

# Read a csv file into a data frame
read_csv(mtcars_path)
# Read lines into a vector
read_lines(mtcars_path)
# Read whole file into a single string
read_file(mtcars_path)
```
See vignette("column-types") on how readr parses columns, and how you can override the defaults.

#### Output

- read_csv() produces a data frame with the following properties:

- Characters are never automatically converted to factors (i.e. no more stringsAsFactors = FALSE).

- Valid column names are left as is, not munged into valid R identifiers (i.e. there is no check.names = TRUE). Missing column names are filled in with X1, X2 etc, and duplicated column names are deduplicated.

- The data frame is given class c("tbl_df", "tbl", "data.frame") so if you also use dplyr you'll get an enhanced display.

- Row names are never set.
