
readr
======================================

The goal of readr is to provide a fast and friendly way to read rectangular data (like csv, tsv, and fwf). It is designed to flexibly parse many types of data found in the wild, while still cleanly failing when data unexpectedly changes. 
The goal of ***readr*** is to provide a fast and friendly way to read tabular data into R.  

<hr>

The most important functions are:

- Read delimited files: `read_delim()`, `read_csv()`, `read_tsv()`, `read_csv2()`.
- Read fixed width files: `read_fwf()`, `read_table()`.
- Read lines: `read_lines()`.
- Read whole file: `read_file()`.
- Re-parse existing data frame: `type_convert()`.


readr supports seven file formats with seven `read_` functions:

- `read_csv()`: comma separated (CSV) files
- `read_tsv()`: tab separated files
- `read_delim()`: general delimited files
- `read_fwf()`: fixed width files
- `read_table()`: tabular files where colums are separated by white-space.
- `read_log()`: web log files

#### Installation

readr is now available from CRAN.

```{r}
install.packages("readr")
You can try out the dev version with:

# install.packages("devtools")
devtools::install_github("hadley/readr")
```
#### Usage

```{r}
library(readr)
library(dplyr)

mtcars_path <- tempfile(fileext = ".csv")
write_csv(mtcars, mtcars_path)

# Read a csv file into a data frame
read_csv(mtcars_path)
# Read lines into a vector
read_lines(mtcars_path)
# Read whole file into a single string
read_file(mtcars_path)
```

#### Output

- `read_csv()` produces a data frame with the following properties:

- Characters are never automatically converted to factors (i.e. no more `stringsAsFactors = FALSE`).

- Valid column names are left as is, not munged into valid R identifiers (i.e. there is no `check.names = TRUE`). 

- Missing column names are filled in with X1, X2 etc, and duplicated column names are deduplicated.

- The data frame is given class `c("tbl_df", "tbl", "data.frame")` so if you also use dplyr you'll get an enhanced display.

- Row names are never set.

#### Compared to base functions

- Compared to the corresponding base functions, readr functions:

- Use a consistent naming scheme for the parameters (e.g. `col_names` and `col_types` not header and colClasses).

- Are much faster (up to 10x faster).

- Have a helpful progress bar if loading is going to take a while.

- All functions work exactly the same way regardless of the current locale. To override the US-centric defaults, use locale().

#### Compared to `fread()`

- data.table has a function similar to read_csv() called fread. Compared to fread, readr:

- Is slower (currently ~1.2-2x slower. If you want absolutely the best performance, use `data.table::fread()`.

- Readr has a slightly more sophisticated parser, recognising both doubled ("""") and backslash escapes ("""). Readr allows you to read factors and date times directly from disk.

- `fread()` saves you work by automatically guessing the delimiter, whether or not the file has a header, how many lines to skip by default and more. Readr forces you to supply these parameters.

- The underlying designs are quite different. Readr is designed to be general, and dealing with new types of rectangular data just requires implementing a new tokenizer. `fread()` is designed to be as fast as possible. `fread()` is pure C, readr is C++ (and Rcpp).
