Specifying the Model
============================
The first step is to define what type of model we would like to use. For our case, we are going to start our analysis with a linear regression but we will demonstrate how we can try different models.

See here for modeling options in parsnip.

```{r}
PM_model <- parsnip::linear_reg() # PM was used in the name for particulate matter
PM_model
## Linear Regression Model Specification (regression)
```

OK. So far, all we have defined is that we want to use a linear regression…Let’s tell parsnip more about what we want.

We would like to use the ordinary least squares method to fit our linear regression. 

### Setting the Engine

So we will tell parsnip that we want to use the ***lm*** package to implement our linear regression (there are 
many options actually such as rstan glmnet, keras, and sparklyr). 
See here for a description of the differences and using these different engines with parsnip.

We will do so by using the <tt>set_engine()</tt> function of the parsnip package.

```{r}
lm_PM_model <- 
  PM_model  %>%
  parsnip::set_engine("lm")

lm_PM_model
````

Here, we aim to predict the air pollution. You can do this with the <tt>set_mode()</tt> function of the parsnip package, by using either set_mode("classification") or set_mode("regression").
```{r}
lm_PM_model <- 
  PM_model  %>%
  parsnip::set_engine("lm") %>%
  set_mode("regression")

lm_PM_model
```

---------------------

### Buidling a Workflow

Now we will use the workflows package to keep track of both our preprocessing steps and our model specification. 
It also allows us to implement fancier optimizations in an automated way.

If you recall novel_rec is the recipe we previously created with the ***recipes*** package and lm_PM_model was created when we specified our model with the parsnip package. Here, we combine everything together into a workflow.

```{r}
PM_wflow <-workflows::workflow() %>%
           workflows::add_recipe(novel_rec) %>%
           workflows::add_model(lm_PM_model)
PM_wflow
```

Ah, nice. Notice how it tells us about both our preprocessing steps and our model specifications.

Next, we “prepare the recipe” (or estimate the parameters) and fit the model to our training data all at once. 
Printing the output, we can see the coefficients of the model.

```{r}
PM_wflow_fit <- parsnip::fit(PM_wflow, data = train_pm)
## Warning in cor(x, use = use, method = method): the standard deviation is zero
## Warning: The correlation matrix has missing values. 274 columns were excluded
## from the filter.
PM_wflow_fit
```




